A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-24 analysis/paper.Rmd
minor change

For the calculation of bias, we used the formula provided in the original paper. 
$$Relative bias = \frac{IE_{survivors} - IE_{survivors,HIV deaths}}{IE_{survivors,HIV deaths}}$$

$$Absolute bias = IE_{survivors} - IE_{survivors,HIV deaths}$$
According to [@quattrochi2019], $IE_{survivor}$ was the estimates of U5M based on living women in 2010, and $IE_{survivors,HIV deaths}$ was the estimates of U5M based on living women in 2010 and women died from HIV/AIDS before 2010 given the condition that they would have been 15-49 in 2010 if they had survived. 
$a_{d}$

@@

Our implementation of the model to estimate the bias in U5M in HIV/AIDS affected populations from @quattrochi2019 was able to replicate the process and output target tables and figures.  Consistently, indirect methods underestimate U5M in older populations, while little difference was shown in younger age groups between unadjusted and adjusted estimates. Applying our model to 2010 survey data from Malawi and Tanzania, we show that indirect methods would underestimate U5M by up to 12%.

>>>>

For the calculation of bias, we used the formula provided in the original paper. 
$$\mbox{Relative bias} = \frac{IE_{survivors} - IE_{survivors,HIV deaths}}{IE_{survivors,HIV deaths}}$$

$$\mbox{Absolute bias} = IE_{survivors} - IE_{survivors,HIV deaths}$$
According to [@quattrochi2019], $IE_{survivor}$ was the estimates of U5M based on living women in 2010, and $IE_{survivors,HIV deaths}$ was the estimates of U5M based on living women in 2010 and women died from HIV/AIDS before 2010 given the condition that they would have been 15-49 in 2010 if they had survived. 
$a_{d}$

@@

Our implementation of the model to estimate the bias in U5M in HIV/AIDS affected populations from @quattrochi2019 was able to replicate the process and output target tables and figures.  Consistently, indirect methods underestimate U5M in older populations, while little difference was shown in younger age groups between unadjusted and adjusted estimates. Applying our model to 2010 survey data from Malawi and Tanzania, we show that indirect methods would underestimate U5M by up to 7%.
